---
title: "a-Help during package development"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a-Help during package development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setuprmd, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load package {attachment}
```{r}
library(attachment)
```

## Use "dev/dev_history.R"

When building your package, create a file called "dev_history.R" in a "dev/" directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("dev")
```

You can then call {attachment} in this file to help you build your description file.

## Fill your DESCRIPTION file

What you really want is to fill and update your description file along with the modifications of your documentation. Indeed, only this function will really be called in your "dev/dev_history.R".  
Run `attachment::att_amend_desc()` each time before `devtools::check()`, this will save you some warnings and errors !

```{r, eval=FALSE}
att_amend_desc()
```

## Change default parameters

We recommend to store the {attachment} command in a "dev/dev_history.R" file in your package, so that you can update the parameters if not using the default ones.

### Use the configuration file

If you run `att_amend_desc()` directly in the console, it will use the last set of parameters run the last time you updated the configuration file.  
Hence, you can change the command in your "dev/dev_history.R" with `update.config = TRUE`, so that next time, you can run `attachment::att_amend_desc()` directly in the console using these updated parameters.

### Ignore some of the dependencies automatically detected

```{r, eval=FALSE}
att_amend_desc(pkg_ignore = c("fakepackage.to_ignore", "other.package"), update.config = TRUE)
```

### Add extra `Suggests` dependencies

```{r, eval=FALSE}
att_amend_desc(extra.suggests = c("suggested.package.not.detected"), update.config = TRUE)
```

### Move detected dependencies from `Imports` to `Suggests`

```{r, eval=FALSE}
att_amend_desc(pkg_ignore = c("package.to.move"), extra.suggests = c("package.to.move"), update.config = TRUE)
```

Next time, you can run `attachment::att_amend_desc()` without any parameters, it will use the config file.

## A package was not detected by `att_amend_desc`

### I have a Rmarkdown file / Quarto file in my "inst/" directory

In your package, you can have a wrapper around `knitr::knit()` with a specific template that you store in "inst/". 
In this case, {attachment} will not detect if there are important dependencies that you used inside your notebook file that are necessary for your package to work properly. Indeed, we can not anticipate if dependencies listed in files in "inst/" need to be in "Imports", "Suggests", or not listed, depending on your use of these files.

For instance, I have a notebook file "inst/my_template.Rmd" as follows, with {bookdown} being used only there in my package:

````
---
title: "My Super template"
author: "John Doe"
date: "`r Sys.Date()`"
output: bookdown::html_document2
---

# First title

My text here.
````

_Suggests_ - If I want to present this template in an example only, {bookdown} should be listed in "Suggests". Then I can run this once:

```{r, eval=FALSE}
att_amend_desc(extra.suggests = c("bookdown"), update.config = TRUE)
```

_Imports_ - If I want to knit it inside a major function of my package, it is recommended to declare the dependency in the 'roxygen' documentation of this function. 

```{r, eval=FALSE}
#' Knit my internal template
#'
#' @importFrom bookdown html_document2
#' @export
#'
my_knit <- function() {
  rmarkdown::render(system.file("my_template.Rmd", package = "my.package"))
}
```

Then I can directly run `att_amend_desc()`.

In the _Imports_ case, if for any reason I decide to delete this `my_knit()` function, then the {bookdown} dependency won't be needed anymore, and {attachment} will automatically remove it with the next `att_amend_desc()`


## Example on a fake package

If you are running this inside a Rmd like here, you may need parameter `inside_rmd = TRUE`.  

```{r}
# Copy package in a temporary directory
tmpdir <- tempfile(pattern = "insidermd")
dir.create(tmpdir)
file.copy(system.file("dummypackage",package = "attachment"), tmpdir, recursive = TRUE)
dummypackage <- file.path(tmpdir, "dummypackage")
# browseURL(dummypackage)
att_amend_desc(path = dummypackage, inside_rmd = TRUE, update.config = TRUE)

# Clean temp files after this example
unlink(tmpdir, recursive = TRUE)
```

## Propose content for "Remotes" field

`set_remotes_to_desc()` adds packages that were installed from other source than CRAN to `Remotes:` field in DESCRIPTION.  

For instance:

- For GitHub: `Remotes: thinkr-open/attachment`
- For GitLab: `Remotes: gitlab::jimhester/covr`
- For Git: `Remotes: git::https://theurl/package_git.git`
- For local package: `Remotes: local::c:\mylocalpackage` or `Remotes: local::subdir/mylocalpackage`
- For Bioconductor: `Remotes: bioc::3.3/package_bioc`
- For r-universe: Show a message to inform how to use r-universe with `options`, like `r-universe: need to set options to repos="https://thinkr-open.r-universe.dev"`


You may want to run it after `att_amend_desc()`.

```{r eval=FALSE}
att_amend_desc(dummypackage) %>%
  set_remotes_to_desc()
```

If you only want to find if packages were installed from other source than CRAN, without amending DESCRIPTION, you can use `find_remotes()`.

You can use it on a vector of packages names 
```{r eval=TRUE}
find_remotes(pkg = c("attachment", "desc", "glue"))
```

You may also want to combine it to `att_from_description()`
```{r, eval=FALSE}
att_from_description() %>%
  find_remotes()
```

If you want to get the complete list of packages installed on your computer with non-CRAN repositories:
```{r, eval=FALSE}
find_remotes(list.dirs(.libPaths(), full.names = FALSE, recursive = FALSE))
```

You can test it if you install {fusen} from GitHub or r-universe:

```{r, eval=FALSE}
# From GitHub
remotes::install_github("ThinkR-open/fusen",
                        quiet = TRUE, upgrade = "never")
attachment::find_remotes("fusen")
#> $fusen
#> [1] "ThinkR-open/fusen"

# From r-universe as default repos
install.packages("fusen", repos = "https://thinkr-open.r-universe.dev")
attachment::find_remotes("fusen")
#> r-universe: need to set options to repos="https://thinkr-open.r-universe.dev" 
```


## Create a file for package installation

Once your package is finished. Well, is a package ever finished ? Let's say, once you want to release a version of your package, you may want to deliver the list of dependencies your users will have to install. A little script like `install.packages(c(...all dep...))` would be so nice :

```{r, eval=FALSE}
create_dependencies_file()
```

This file will be placed in `inst/dependencies.R` and contains :

```{r, eval=FALSE}
# No Remotes ----
# remotes::install_github("ThinkR-open/fcuk")
# Attachments ----
to_install <- c("covr", "desc", "devtools", "glue", "knitr", "magrittr", "rmarkdown", "stats", "stringr", "testthat", "utils")
for (i in to_install) {
  message(paste("looking for ", i))
  if (!requireNamespace(i)) {
    message(paste("     installing", i))
    install.packages(i)
  }
}
```

## Other possibilities

Of course, you can also use {attachment} out of a package to list all package dependencies of R scripts using `att_from_rscripts()` or Rmd files using `att_from_rmds()`.

```{r, eval=TRUE}
dummypackage <- system.file("dummypackage", package = "attachment")

att_from_rscripts(path = file.path(dummypackage, "R"))
att_from_rmds(path = file.path(dummypackage, "vignettes"), inside_rmd = TRUE)
```


