---
title: "a-Help during package development"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a-Help during package development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setuprmd, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load package {attachment}
```{r}
library(attachment)
```

## Use "dev/dev_history.R"

When building your package, create a file called "dev_history.R" in a "dev/" directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("dev")
```

You can then call {attachment} in this file to help you build your description file.

## Fill your DESCRIPTION file

What you really want is to fill and update your description file along with the modifications of your documentation. Indeed, only this function will really be called in your "dev/dev_history.R".  
Run `attachment::att_amend_desc()` each time before `devtools::check()`, this will save you some warnings and errors !

```{r, eval=FALSE}
att_amend_desc()
```

#### Example on a fake package

If you are running this inside a Rmd like here, you may need parameter `inside_rmd = TRUE`.  

```{r}
# Copy package in a temporary directory
tmpdir <- tempdir()
file.copy(system.file("dummypackage",package = "attachment"), tmpdir, recursive = TRUE)
dummypackage <- file.path(tmpdir, "dummypackage")
# browseURL(dummypackage)
att_amend_desc(path = dummypackage, inside_rmd = TRUE)
```

## Propose content for "Remotes" field

`set_remotes_to_desc()` adds packages that were installed from other source than CRAN to `Remotes:` field in DESCRIPTION.  

For instance:

- For GitHub : `Remotes: thinkr-open/attachment`
- For GitLab : `Remotes: gitlab::jimhester/covr`

You may want to run it after `att_amend_desc()`.

```{r eval=FALSE}
att_amend_desc(dummypackage) %>%
  set_remotes_to_desc()
```

If you only want to find if packages were installed from other source than CRAN, without amending DESCRIPTION, you can use `find_remotes()`.

You can use it on a vector of packages names 
```{r eval=TRUE}
find_remotes(pkg = c("attachment", "desc", "glue"))
```

You may also want to combine it to `att_from_description()`
```{r, eval=FALSE}
att_from_description() %>%
  find_remotes()
```

## Create a file for package installation
Once your package is finished. Well, is a package ever finished ? Let's say, once you want to release a version of your package, you may want to deliver the list of dependencies your users will have to install. A little script like `install.packages(c(...all dep...))` would be so nice :

```{r, eval=FALSE}
create_dependencies_file()
```

This file will be placed in `inst/dependencies.R` and contains :

```{r, eval=FALSE}
# No Remotes ----
# remotes::install_github("ThinkR-open/fcuk")
# Attachments ----
to_install <- c("covr", "desc", "devtools", "glue", "knitr", "magrittr", "rmarkdown", "stats", "stringr", "testthat", "utils")
for (i in to_install) {
  message(paste("looking for ", i))
  if (!requireNamespace(i)) {
    message(paste("     installing", i))
    install.packages(i)
  }
}
```

## Other possibilities

Of course, you can also use {attachment} out of a package to list all package dependencies of R scripts using `att_from_rscripts()` or Rmd files using `att_from_rmds()`.

```{r, eval=TRUE}
dummypackage <- system.file("dummypackage", package = "attachment")

att_from_rscripts(path = file.path(dummypackage, "R"))
att_from_rmds(path = file.path(dummypackage, "vignettes"), inside_rmd = TRUE)
```


