---
title: "b-bookdown and other scripts dependencies"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{b-bookdown and other scripts dependencies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setuprmd, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load package {attachment}
```{r}
library(attachment)
```

## Use "dev/dev_history.R"

When building your package, create a file called "dev_history.R" in a "dev/" directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("dev")
```

You can then call {attachment} in this file to help you build your description file.

## Fill a bookdown DESCRIPTION file

You can use a similar approach for a {bookdown} description file using `attachment::att_to_desc_from_is()`.
Indeed, you can use it in your CI to automatically build your HTML pages while parsing dependencies required. Note that to include it directly in CI (as proposed in {gitlabr} templates), you may need to set `att_to_desc_from_is(must.exist = FALSE)`.

```{r, eval=FALSE}
# bookdown Imports are in Rmds
imports <- c("bookdown", attachment::att_from_rmds("."))

attachment::att_to_desc_from_is(
  path.d = "DESCRIPTION",
  imports = imports, suggests = NULL, 
  must.exist = FALSE
)
```

Then, you can install dependencies from the DESCRIPTION file.

```{r, eval=FALSE}
remotes::install_local()
```

### Propose content for "Remotes" field

An interest of using DESCRIPTION to list your bookdown dependencies is to use packages from other sources than CRAN and list them in the 'Remotes' field.  
Here comes `set_remotes_to_desc()`, which adds packages that were installed from other source than CRAN to `Remotes:` field in DESCRIPTION.  

You can run it after `att_to_desc_from_is()`.

```{r eval=FALSE}
attachment::att_to_desc_from_is(
  path.d = "DESCRIPTION",
  imports = imports, suggests = NULL, 
  must.exist = FALSE
) %>%
  set_remotes_to_desc()
```


## Get all packages listed in "namespace"
You can get the list of packages in your package with `att_from_namespace()`

```{r, eval=FALSE}
att_from_namespace()
```

## Get all packages added using `pkg::function` or library/require
This reads all files in directories of R scripts (default to `R` directory of a package)

```{r, eval=FALSE}
att_from_rscripts()
```

## Get all packages called in your Rmd
If you have vignette, you may want to list extra libraries, not listed in your "Depends" list. This function applies to any Rmd file, of course.

```{r, eval=FALSE}
att_from_rmds()
```


## Get all packages called in your Rmd and show them in this same Rmd

Of course, you can also use {attachment} out of a package to list all package dependencies of R scripts using `att_from_rscripts()` or Rmd files using `att_from_rmds()`.  
If you want to run `att_from_rmds()` inside a Rmd as for this vignette, you will need to set `att_from_rmds(inside_rmd = TRUE)`

```{r, eval=TRUE}
dummypackage <- system.file("dummypackage", package = "attachment")

att_from_rmds(path = file.path(dummypackage, "vignettes"), inside_rmd = TRUE)
```


