---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load package {attachment}
```{r}
library(attachment)
# library(test)
```

# Use "devstuff_history.R"

When building your package, create a file called "devstuff_history.R" in the root directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("devstuff_history.R")
```

You can then call {attachment} in this file to help you build your namespace.

# Get all packages listed in "namespace"
After running `devtools::document()`, you can get the list of packages in your package with `att_from_namespace()`

```{r, eval=FALSE}
att_from_namespace()
```

# Get all packages called in your vignettes
If you have vignette, you may want to list extra libraries, not listed in your "Depends" list.

```{r, eval=FALSE}
att_from_vignettes()
```

# Fill your DESCRIPTION file
Of course, what you really want is to fill and update your description file along with the modifications of your documentation. Indeed, only this function will really be called in your "devstuff_history.R"

```{r, eval=FALSE}
att_to_description()
```


