---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load package {attachment}
```{r}
library(attachment)
```

## Use "devstuff_history.R"

When building your package, create a file called "devstuff_history.R" in the root directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("devstuff_history.R")
```

You can then call {attachment} in this file to help you build your namespace.

## Get all packages listed in "namespace"
You can get the list of packages in your package with `att_from_namespace()`

```{r, eval=FALSE}
att_from_namespace()
```

## Get all packages added using `pkg::function`
This read all files in the `R` directory.

```{r, eval=FALSE}
att_from_functions()
```

## Get all packages called in your vignettes
If you have vignette, you may want to list extra libraries, not listed in your "Depends" list.

```{r, eval=FALSE}
att_from_vignettes()
```

## Fill your DESCRIPTION file
Of course, what you really want is to fill and update your description file along with the modifications of your documentation. Indeed, only this function will really be called in your "devstuff_history.R"

```{r, eval=FALSE}
att_to_description()
```

## Create a file for package installation
Once your package is finished. Well, is a package ever finished ? Let's say, once you want to release a version of your package, you may want to deliver the list of dependencies your users will have to install. A little script like `install.packages(c(...all dep...))` would be so nice :

```{r, eval=FALSE}
get_dependencies()
```


