---
title: "Extract scripts dependencies and generate your Description file"
author: "Sébastien Rochette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extract scripts dependencies and generate your Description file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setuprmd, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load package {attachment}
```{r}
library(attachment)
```

## Use "devstuff_history.R"

When building your package, create a file called "devstuff_history.R" in the root directory. You will store all "manual" calls to `devtools::xxx` and `usethis::xxx` in this script.  
Its first line should be :

```r
usethis::use_build_ignore("devstuff_history.R")
```

You can then call {attachment} in this file to help you build your description file.

## Fill your DESCRIPTION file
### For packages
What you really want is to fill and update your description file along with the modifications of your documentation. Indeed, only this function will really be called in your "devstuff_history.R".  
Run `attachment::att_amend_desc()` each time before `devtools::check()`, this will save you some warnings and errors !

```{r, eval=FALSE}
att_amend_desc()
```

#### Example on a fake package

If you are running this inside a Rmd like here, you may need parameter `inside_rmd = TRUE`.  

```{r}
# Copy package in a temporary directory
tmpdir <- tempdir()
file.copy(system.file("dummypackage",package = "attachment"), tmpdir, recursive = TRUE)
dummypackage <- file.path(tmpdir, "dummypackage")
# browseURL(dummypackage)
att_amend_desc(path = dummypackage, inside_rmd = TRUE)
```

### For bookdown
You can use a similar approach for a {bookdown} description file using `attachment::att_to_desc_from_is()`

```{r, eval=FALSE}
# bookdown Imports are in Rmds
imports <- c("bookdown", attachment::att_from_rmds("."))
attachment::att_to_desc_from_is(path.d = "DESCRIPTION",
                                imports = imports, suggests = NULL)
```

### Propose content for "Remotes" field

`find_remotes()` checks if packages were installed from other source than CRAN. 
If so, it returns the content you can add to `Remotes:` field in DESCRIPTION.
For instance:

- For GitHub : `Remotes: thinkr-open/attachment`
- For GitLab : `Remotes: gitlab::jimhester/covr`

You probably want to combine it to `att_from_description()`
```{r, eval=FALSE}
att_from_description() %>% find_remotes()
```


## Get all packages listed in "namespace"
You can get the list of packages in your package with `att_from_namespace()`

```{r, eval=FALSE}
att_from_namespace()
```

## Get all packages added using `pkg::function` or library/require
This reads all files in directories of R scripts (default to `R` directory of a package)

```{r, eval=FALSE}
att_from_rscripts()
```

## Get all packages called in your Rmd
If you have vignette, you may want to list extra libraries, not listed in your "Depends" list. This function applies to any Rmd file, of course.

```{r, eval=FALSE}
att_from_rmds()
```

## Create a file for package installation
Once your package is finished. Well, is a package ever finished ? Let's say, once you want to release a version of your package, you may want to deliver the list of dependencies your users will have to install. A little script like `install.packages(c(...all dep...))` would be so nice :

```{r, eval=FALSE}
create_dependencies_file()
```

This file will be placed in `inst/dependencies.R` and contains :

```{r, eval=FALSE}
# No Remotes ----
# remotes::install_github("ThinkR-open/fcuk")
# Attachments ----
to_install <- c("covr", "desc", "devtools", "glue", "knitr", "magrittr", "rmarkdown", "stats", "stringr", "testthat", "utils")
for (i in to_install) {
  message(paste("looking for ", i))
  if (!requireNamespace(i)) {
    message(paste("     installing", i))
    install.packages(i)
  }
}
```

## Other possibilities

Of course, you can also use {attachment} out of a package to list all package dependencies of R scripts using `att_from_rscripts()` or Rmd files using `att_from_rmds()`.

```{r, eval=TRUE}
dummypackage <- system.file("dummypackage", package = "attachment")

att_from_rscripts(path = file.path(dummypackage, "R"))
att_from_rmds(path = file.path(dummypackage, "vignettes"), inside_rmd = TRUE)
```


